Fractional Types

### 2013-02-21 frac.tex
included diagrams

\newcommand{\inkscape}[2][1.5]{
\begin{center}
\scalebox{#1}{
\includegraphics{diagrams/#2}
}
\end{center}
}

@@

@@

@@

@@

@@

\begin{example}[Annihilation]
\label{ch3:ex;annihilation}
Consider the circuit below:
\begin{center}
\scalebox{1.2}{
  \includegraphics{diagrams/not_trace.pdf}
}
\end{center}
As motivated earlier, it is clearly impossible for the constraint implied by
{{trace*}} to be satisfied as a boolean value {{v}} can never be the same as
its negation. Thus there is no incoming value of type {{b}} that can ever go
through the circuit. Indeed, if we call the circuit above {{c}}, then we can
calculate that {{c}} does not relate {{v}} to anything. We call such a
circuit an annihilation circuit.
\end{example}

>>>>

\newcommand{\dgm}[2][1.5]{
\begin{center}
\scalebox{#1}{
\includegraphics{diagrams/#2.pdf}
}
\end{center}
}

@@

\begin{multicols}{2}
  \dgm{eta_times2}

  \dgm{eps_times2}  
\end{multicols}

@@

\begin{multicols}{2}
  \dgm{function-times}

  \dgm{delimc-times}
\end{multicols}

@@

\begin{multicols}{2}
  \dgm[1.2]{apply-times1}

  \dgm{apply-times2}
\end{multicols}

@@

\begin{multicols}{2}
  \dgm[1.0]{compose-times1}

  \dgm{compose-times2}
\end{multicols}

\dgm{compose-times3}

@@

\begin{example}[Annihilation]
\label{ch3:ex;annihilation}
Consider the circuit below:
\dgm{not_trace}
As motivated earlier, it is clearly impossible for the constraint implied by
{{trace*}} to be satisfied as a boolean value {{v}} can never be the same as
its negation. Thus there is no incoming value of type {{b}} that can ever go
through the circuit. Indeed, if we call the circuit above {{c}}, then we can
calculate that {{c}} does not relate {{v}} to anything. We call such a
circuit an annihilation circuit.
\end{example}
